\documentclass[10pt,a4paper, notitlepage]{report}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{svg}
\usepackage{float}

\title{PhD Proposal}
\author{Irvin Aloise}


\begin{document}
\maketitle


\textbf{Keywords.} \textit{Mobile Robotics, SLAM, Multi-Agent and Multi-Robot Systems}


\section*{Summary of Proposal}
Todo


\section*{State of the Art}
In Robotics, an autonomous agent performs Simultaneous Localization and Mapping (SLAM) when it builds a map of the environment using different kind of sensors while localizing itself in the created map. Its core is a complex non-linear mathematical problem and it has been studied since 80s \cite{durrant2006simultaneous} \cite{bailey2006simultaneous}; during this early stage, statistical basis that will constitute SLAM's core were investigated. Only in late 90s probabilistic approaches started to spread, mainly based on \textit{Extended Kalman Filters} \cite{leonard1990dynamic} \cite{dissanayake2001solution} and \textit{Expectation Maximization} algorithms \cite{dellaert2003mcmc} \cite{thrun2001probabilistic}. Filtering continued to gain popularity with \textit{Particle Filters} - employed in the remarkable work of \textit{Montemerlo et al.} \cite{montemerlo2002fastslam} - and its future refinements, like \textit{Rao-Blackwellized Particle Filters} \cite{grisetti2005improving} \cite{carlone2010rao} \cite{tipaldi2007heterogeneous}.

Filtering-based approaches bring multiple drawbacks, like low computational efficiency and low accuracy due to problem's high nonlinearities; for these reasons, \textit{Maximum A Posteriori} (MAP) algorithms started to gain popularity and a step back to the solution of Lu \textit{et al.} \cite{lu1997globally} has been done. Exploiting more powerful computing resources, the problem can be formalized as an \textit{hyper-graph} where each node represents a robot pose or a landmark - a point of interest placed in the robot's surrounding - and each hyper-edge represents a constraint between a subset of nodes. 

Exploiting graph's topology, factor-graph optimization can achieve impressive performances as stated in the works of Dallaert \textit{et al.} \cite{dellaert2006square} and Kummerle \textit{et al.}  \cite{kummerle2011g}. MAP optimizers \cite{kummerle2011g} \cite{dellaert2012gtsam} \cite{ceres-solver} \cite{kaess2012isam2} are able to easily deal with huge graph and incremental optimization, delivering state-of-the-art performances both in speed and accuracy terms.

While SLAM's back-end performs map optimization, graph population is done by system's front-end, exploiting sensors' measurements. State-of-the-art systems usually acquire data from cameras (RGB or RGB-D) or 3D-LiDARs. The former ones in particular are gaining much attention since they are cheap and can be mounted basically on every kind of robot - in single or stereo configurations. Current benchmark systems for \textit{monocular visual SLAM} are \textit{ORB-SLAM} \cite{mur2015orb-slam} and \textit{LSD-SLAM} \cite{engel2014lsd-slam}, while for \textit{stereo configurations} it is impossible to ignore \textit{ORB-SLAM2} \cite{mur2017orb-slam2}. The former and the latter systems rely on the extraction of visual features from the scene, making them vulnerable to light changes or untextured scenes. \textit{LSD-SLAM} instead uses raw data to track robot motion and, thus, it is more robust to such weakness at the cost of more computational power needed to deliver real-time performances.

All those systems - even if they are able to produce significant results in terms of accuracy and speed - share one big drawback: the \textit{lack of scalability} that would allow to cope with real-world scenarios. In this sense, the research community is still far from a solution, even if some early attempts are made. Possible approaches to scalability that can be found in literature are based on \textit{node - edge sparsification} \cite{kretzschmar2011graph-pruninig} \cite{huang2013consistent} - that consists in pruning less informative node or factors following a suitable criterion - \textit{parallelization of SLAM system} \cite{ni-dallaert2010nested-dissections} \cite{ni-dallaert2007tectonicSAM} \cite{grisetti2010hogman} or \textit{multi-robot SLAM} \cite{cunningham2013ddfSAM2} \cite{lazaro2013mr-slam}. All those approaches are too early and still miss the point on long-term scalability issues like \textit{robustness}, the possibility to run with \textit{limited resources} and \textit{efficient data storage methods}. It is good to notice that a scalable SLAM system, besides all those features, has to operate in different environments, thus adaptation must be taken in consideration to avoid failures - e.g. map representation adaptation, system's parameters auto-tuning to different environmental conditions - but none of the existing SLAM system provides such competences.

\section*{Research Objectives}
Simultaneous Localization and Mapping is a well known topic in Robotics and the research community has done many steps forward, but still there are many problems unsolved and not yet well investigated. System's scalability is one this open issues. 

Scalability is the first step towards \textit{long-range SLAM}, allowing the robot to operate for long periods without saturating system's resources. It has been demonstrated that using \textit{direct linear solvers}, factor-graphs grow quadratically with the number of variables; moreover, loop-closures cause a lessening of the problem sparsity, leading to more computational-heavy optimization steps. With this in mind, graph efficiency must by seriously improved in order to let the system run properly. \textit{Sub-graph partitioning} \cite{grisetti2012condensed-m} represents a good starting point to achieve results in this direction. For example, compress and off-load parts of the graph that are not relevant for the current state of the robot may lead to an easier optimization from a computational point of view. Of course, this means to perform non-global optimization, thus, convergence's quality must be also considered.

\section*{Results, impacts and benefits}
Todo




\bibliographystyle{unsrt}
\bibliography{bibliography}

\end{document}